Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-03-30 talk/icooolps2011/paper.tex
nonsense

For space reasons we cannot perform a full evaluation here, but still want to
present some benchmark numbers. We chose to present two benchmarks, a port of
the classical Richards benchmark in RPython and a Python version of the Telco
decimal benchmark\footnote{\texttt{http://speleotrove.com/decimal/telco.html}},
using a pure Python decimal floating point implementation.

>>>>

For space reasons we cannot perform a full evaluation here, but still want to
present some benchmark numbers. We chose to present two benchmarks, a port of
the classical Richards benchmark in Python and a Python version of the Telco
decimal benchmark\footnote{\texttt{http://speleotrove.com/decimal/telco.html}},
using a pure Python decimal floating point implementation.
